---
title: "Advanced_calibration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced_calibration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cali)
library(malariasimulation)
library(ggplot2)
```
We've seen how to perform a very simple calibration. Here we will look at more
advanced options. To start with lets define a new summary function, this one will
produce a vector of annual average estimates of prevalence in 2-10 year olds:

```{r}
annual_pfpr_summary <- function(x){
  year <- ceiling(x$timestep / 365)
  pfpr <- x$n_detect_730_3650 / x$n_730_3650
  tapply(pfpr, year, mean)
}
```

We can use this function to calibrate against multiple years of PfPr estimates:

```{r}
target <- c(0.3, 0.2, 0.1)

parameters <- get_parameters() |>
  set_bednets(
    timesteps = 365 * 0:2,
    coverages = c(0, 0.3, 0.4),
    retention = 5 * 365,
    dn0 = matrix(0.53, nrow = 3, ncol = 1),
    rn = matrix(0.56, nrow = 3, ncol = 1),
    rnm = matrix(0.24, nrow = 3, ncol = 1),
    gamman = rep(2.64 * 365, 3)
  )
parameters$timesteps <- 365 * 3

set.seed(123)
out <- calibrate(
  parameters = parameters,
  target = target,
  summary_function = annual_pfpr_summary,
  eq_prevalence = target[1]
)

parameters$human_population <- 5000
parameters <- set_equilibrium(parameters, init_EIR = out)
raw <- run_simulation(parameters$timesteps + 100, parameters = parameters)
raw$pfpr <- raw$n_detect_730_3650 / raw$n_730_3650

ggplot() +
  geom_point(aes(x = 365 * (0:2 + 0.5), y = target), col = "dodgerblue", size = 4) + 
  geom_line(data = raw, aes(x = timestep, y = pfpr), col = "deeppink", linewidth = 1) +
  ylim(0, 1) +
  ylab(expression(italic(Pf)*Pr[2-10])) +
  xlab("Time") +
  theme_bw()
```

# Population size
There is no single correct answer to the question "what modelled population size
should I use?". In our pursuit of efficiency during the calibration process, 
it is our preference to begin with a modestly sized modelled population.
This approach, however, requires a balance: the population must be sufficiently
large to ensure that the level of stochastic noise remains within acceptable bounds
and avoid unwanted elimination due to stochastic fade-out. If unwanted elimination
occurs (where any output = 0 and taregt != 0), the algoritm will first increase 
the human population size to the subsequent larger value specified in the 
`human_population` argument. 

You must be happy with the level of stochastic in a run with the smallest
values in the `human_popualation` argument. 

We can see this occuring below:

```{r}
# Define target, here a prevalence measures:
target <- 0.001
parameters <- get_parameters()
parameters$timesteps <- 365 * 3
set.seed(123)
out <- calibrate(
  parameters = parameters,
  target = target,
  summary_function = summary_mean_pfpr_2_10,
  eq_prevalence = target,
  human_population = c(100, 1000, 10000)
)
```

# EIR initialisation
To provide a reasonable starting guess for the calibration, we use the malaria
model equilibrium solution to match to a baseline PfPr `eq_prevalence` given a
level of treatment coverage `eq_ft`. A good initialised EIR will mean that the
algorithm converges more quickly, but isn't necessary. If you don't know
`eq_prevalence` or `eq_ft`, try with a reasonable guess.

# Weighting target values
There may be a situation where there is more evidence to support some 
specific target data over other. In this situation we can weight our target and
summary function to bias our fitting more towards or away from certain points.

```{r}
target <- c(0.5, 0.2, 0.1)
weights = c(0.1, 1, 1)
weighted_target <- target * weights

weighted_annual_pfpr_summary <- function(x, w = weights){
  year <- ceiling(x$timestep / 365)
  pfpr <- x$n_detect_730_3650 / x$n_730_3650
  tapply(pfpr, year, mean) * w
}

parameters <- get_parameters() |>
  set_bednets(
    timesteps = 365 * 0:2,
    coverages = c(0, 0.3, 0.4),
    retention = 5 * 365,
    dn0 = matrix(0.53, nrow = 3, ncol = 1),
    rn = matrix(0.56, nrow = 3, ncol = 1),
    rnm = matrix(0.24, nrow = 3, ncol = 1),
    gamman = rep(2.64 * 365, 3)
  )
parameters$timesteps <- 365 * 3

set.seed(123)
out <- calibrate(
  parameters = parameters,
  target = weighted_target,
  summary_function = weighted_annual_pfpr_summary,
  eq_prevalence = target[1]
)

parameters$human_population <- 5000
parameters <- set_equilibrium(parameters, init_EIR = out)
raw <- run_simulation(parameters$timesteps + 100, parameters = parameters)
raw$pfpr <- raw$n_detect_730_3650 / raw$n_730_3650

ggplot() +
  geom_point(aes(x = 365 * (0:2 + 0.5), y = target), col = "dodgerblue", size = 4) + 
  geom_line(data = raw, aes(x = timestep, y = pfpr), col = "deeppink", linewidth = 1) +
  ylim(0, 1) +
  ylab(expression(italic(Pf)*Pr[2-10])) +
  xlab("Time") +
  theme_bw()
```