---
title: "Advanced_calibration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced_calibration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cali)
library(malariasimulation)
library(ggplot2)
```
We've seen how to perform a very simple calibration. Here we will look some more
advanced options. To start with lets define a new summary function, this one will
produce a vector of annual average estimates of prevalence in 2-10 year olds:

```{r}
annual_pfpr_summary <- function(x){
  year <- ceiling(x$timestep / 365)
  pfpr <- x$n_detect_730_3650 / x$n_730_3650
  tapply(pfpr, year, mean)
}
```

We can use this function to calibrate against multiple years of PfPr estimates:

```{r}
target <- c(0.3, 0.2, 0.1)

parameters <- get_parameters(list(human_population = 5000, individual_mosquitoes = FALSE)) |>
  set_bednets(
    timesteps = 365 * 0:2,
    coverages = c(0, 0.3, 0.4),
    retention = 5 * 365,
    dn0 = matrix(0.53, nrow = 3, ncol=1),
    rn = matrix(0.56, nrow = 3, ncol=1),
    rnm = matrix(0.24, nrow = 3, ncol=1),
    gamman = rep(2.64 * 365, 3)
  )
parameters$timesteps <- 365 * 3

set.seed(123)
out <- calibrate(parameters = parameters,
                 target = target,
                 summary_function = annual_pfpr_summary,
                 tolerance = 0.01, 
                 interval = c(4, 6))

parameters <- set_equilibrium(parameters, init_EIR = out$root)
raw <- run_simulation(parameters$timesteps + 100, parameters = parameters)
raw$pfpr <- raw$n_detect_730_3650 / raw$n_730_3650

ggplot() +
  geom_point(aes(x = 365 * (0:2 + 0.5), y = target), col = "dodgerblue", size = 4) + 
  geom_line(data = raw, aes(x = timestep, y = pfpr), col = "deeppink", size = 1) +
  ylim(0, 1) +
  theme_bw()
```

There may be a situation where there is more evidence to support some specific 
target data over other. In this situation we can supply weights to bias our
fitting more towards or away from certain points.

```{r}
target <- c(0.5, 0.2, 0.1)

parameters <- get_parameters(list(human_population = 5000, individual_mosquitoes = FALSE)) |>
  set_bednets(
    timesteps = 365 * 0:2,
    coverages = c(0, 0.3, 0.4),
    retention = 5 * 365,
    dn0 = matrix(0.53, nrow = 3, ncol=1),
    rn = matrix(0.56, nrow = 3, ncol=1),
    rnm = matrix(0.24, nrow = 3, ncol=1),
    gamman = rep(2.64 * 365, 3)
  )
parameters$timesteps <- 365 * 3

set.seed(123)
out <- calibrate(parameters = parameters,
                 target = target,
                 summary_function = annual_pfpr_summary,
                 tolerance = 0.01, 
                 interval = c(4, 6),
                 weights = c(0.1, 1, 1))

parameters <- set_equilibrium(parameters, init_EIR = out$root)
raw <- run_simulation(parameters$timesteps + 100, parameters = parameters)
raw$pfpr <- raw$n_detect_730_3650 / raw$n_730_3650

ggplot() +
  geom_point(aes(x = 365 * (0:2 + 0.5), y = target), col = "dodgerblue", size = 4) + 
  geom_line(data = raw, aes(x = timestep, y = pfpr), col = "deeppink", size = 1) +
  ylim(0, 1) +
  theme_bw()
```