---
title: "Basic calibration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic_calibration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cali)
library(malariasimulation)
library(ggplot2)
```

## Calibrate good times, come on!

First, let's define the target we are trying to match to. In this instance, we
want to match to prevalence in 2-10 year olds at two time points:

```{r}
# Define target, here two prevalence measures:
target <- c(0.3, 0.3)
# Time points at which to match target
target_tt <- c(500, 600)
```

You must supply a summary function when calibrating. This function takes the raw
model output and returns a vector (of length timesteps), of your target variable.
For PfPr 2-10, we have a helper function for this `summary_pfpr_2_10()`.

We also need to set up all other aspects of our simulation. In this case, we will
set up a very basic model run:

```{r}
parameters <- malariasimulation::get_parameters(list(human_population = 1000))
```

Now time for the calibration. Here we set the tolerance to 0.02. This means that
the distance between each target value and model output prevalence needs to be <2%. The
tolerance is specified in the unit of the target variable. We also cheat a bit here
and put a tight bound on the EIR to search to help speed up this code.

```{r}
set.seed(123)
out <- calibrate(parameters = parameters,
                 target = target,
                 target_tt = target_tt,
                 summary_function = summary_pfpr_2_10,
                 tolerance = 0.02, 
                 interval = c(1, 6))
```

Ok, we've calibrated. Lets run the calibrated model and see how we did.

```{r}
parameters <- malariasimulation::set_equilibrium(parameters, init_EIR = out$root)
raw <- malariasimulation::run_simulation(timesteps = max(target_tt) + 100, parameters = parameters)
pfpr <- summary_pfpr_2_10(raw)

pd <- data.frame(time = 1:(max(target_tt) + 100), pfpr = pfpr)

ggplot() +
  geom_line(data = pd, aes(x = time, y = pfpr), col = "deeppink", size = 1) +
  geom_point(aes(x = target_tt, y = target), col = "dodgerblue", size = 4) + 
  ylim(0, 1) +
  theme_bw()

```

## Caveats

Note, in many situations it will not be possible to calibrate tightly to targets,
especially over multiple time points. We are just changing the baseline EIR, 
so any trends in targets over time would need to be captured by other aspects of
the simulation set up - for example intervention coverage. Don't expect to be able to
match all data, you'll never match a trend of increasing prevalence over time if
you model run has increasing intervention coverage over time too!